ms_figures

### 2018-03-21 man/ms_figures.Rmd
combine plots

##### 
**Appendix S1** Acumulated monthly precipitation during the hydrological year 2004-2005 (blue line) and 2011-2012 (red line). The boxplot representing the average from 1940-2015 period. Data from meteorological station Granada, Base Aérea (National Spanish Meteorological Services, AEMET).

@@

st5514_pro  %>% 
  filter(!(hyear_f %in% c('2004-2005', '2011-2012'))) %>% 
  ggplot(aes(x=as.factor(hmonth), y=csum)) + 
  geom_boxplot(aes(x=as.factor(hmonth))) +  
  geom_smooth(aes(group=1), se=TRUE, level=0.95, colour='black') + 
  geom_line(data=subset(st5514_pro, hyear_f == '2004-2005'),
            aes(x=as.factor(hmonth), y=csum, group=1), colour='blue') +
  geom_line(data=subset(st5514_pro, hyear_f == '2011-2012'),
            aes(x=as.factor(hmonth), y=csum, group=1),
            colour='red') +
  theme_bw() + 
  theme(strip.background = element_rect(fill = NA, color = "black")) + 
  ylab('Precipitation (mm) acumulated') + xlab('') + 
  ggtitle('Granada Base Aerea, 1950-2015') + 
  scale_x_discrete(labels=c("1"="Sep", "2"="Oct", "3"="Nov", "4"="Dec", "5"="Jan", "6"="Feb",
                            "7"="Mar", "8"="Apr", "9"="May", "10"="Jun", "11"="Jul", "12"="Aug")) +
  annotate("text", label = "2004-2005", x = 2, y = 500, size = 6, colour = "blue") + 
  annotate("text", label = "2011-2012", x = 2, y = 550, size = 6, colour = "red") + 
  annotate("text", label = "mean 1950-2015", x = 3, y = 600, size = 6, colour = "black")
```

@@

##### 
```{r}
prec_files <- list.files(here::here('data_raw/meteo/prec_subclima/'), pattern="*.csv")

prec_hydrol_sn <- ggplot(presn, aes(x=hyear, y=csum_mean)) + 
  geom_hline(yintercept = meandf) + 
  geom_hline(yintercept = meandf + 2*sddf, color ='blue', linetype = 'dashed') +
  geom_hline(yintercept = meandf - 2*sddf, color ='red', linetype = 'dashed') +
  geom_hline(yintercept = meandf + 1*sddf, color ='blue', linetype = 'dotted') +
  geom_hline(yintercept = meandf  - 1*sddf, color ='red', linetype = 'dotted') +
  geom_errorbar(aes(ymin = csum_mean - csum_se, ymax= csum_mean + csum_se), width=.1, colour='gray') +
  geom_point(size=2) + theme_bw() +
  scale_x_continuous(breaks=seq(1950,2020, by=5)) +
  scale_y_continuous(breaks=seq(0,1500, by=250)) +
  geom_text_repel(
    data = subset(presn, csum_mean < (meandf - 1*sddf)),
    aes(label = hyear)) +
  theme(panel.grid.minor = element_blank()) +
  ylab('Cumulative Precipitation (hydrological year)') + xlab('year')
prec_hydrol_sn
```

**Appendix S3.** Temporal evolution of cumulative precipitation (hydrological year) during the period 1950-2017 for 28 meteorological stations (from National Spanish Meteorological Services, AEMET) distributed around the Sierra Nevada area. Points represent mean and errorbars standard error. *Black* line indicates mean for all period. *Red* lines represent -1 (*dotted* line) and -2 (*dashed* line) standard deviation. *Blue* lines represent +1 (*dotted* line) and +2 (*dashed* line) standard deviation. We indicate all years with average values below -1SD.

>>>>

**Appendix S1.** Temporal evolution of cumulative precipitation (hydrological year) during the period 1950-2017 for 28 meteorological stations (from National Spanish Meteorological Services, AEMET) distributed around the Sierra Nevada area. Points represent mean and errorbars standard error. *Black* line indicates mean for all period. *Red* lines represent -1 (*dotted* line) and -2 (*dashed* line) standard deviation. *Blue* lines represent +1 (*dotted* line) and +2 (*dashed* line) standard deviation. We labelled all years with average values below -1SD. ***Inset plot***: cumulative precipitation during the hydrological years 2004-2005 (*blue line*) and 2011-2012 (*red line*). The boxplot representing the average from 1950-2015 period. Data from meteorological station Granada, Base Aérea (National Spanish Meteorological Services, AEMET).

@@

df <- st5514_pro  %>% 
  filter(!(hyear_f %in% c('2004-2005', '2011-2012')))

cp <- ggplot(df, aes(x=as.factor(hmonth), y=csum)) + 
  geom_boxplot(aes(x=as.factor(hmonth))) +  
  geom_smooth(aes(group=1), se=TRUE, level=0.95, colour='black') + 
  geom_line(data=subset(st5514_pro, hyear_f == '2004-2005'),
            aes(x=as.factor(hmonth), y=csum, group=1), colour='blue') +
  geom_line(data=subset(st5514_pro, hyear_f == '2011-2012'),
            aes(x=as.factor(hmonth), y=csum, group=1),
            colour='red') +
  theme_bw() + 
  theme(strip.background = element_rect(fill = NA, color = "black")) + 
  ylab('Cumulative Precipitation (mm)')  + xlab('') + 
  # ggtitle('Granada Base Aerea, 1950-2015') + 
  scale_x_discrete(labels=c("1"="Sep", "2"="Oct", "3"="Nov", "4"="Dec", "5"="Jan", "6"="Feb",
                            "7"="Mar", "8"="Apr", "9"="May", "10"="Jun", "11"="Jul", "12"="Aug")) +
  annotate("text", label = "2004-2005", x = 2, y = 500, size = 4, colour = "blue") + 
  annotate("text", label = "2011-2012", x = 2, y = 550, size = 4, colour = "red") + 
  annotate("text", label = "mean 1950-2015", x = 3, y = 600, size = 4, colour = "black") +
  theme(panel.grid = element_blank())
```

```{r}
prec_files <- list.files(here::here('data_raw/meteo/prec_subclima/'), pattern="*.csv")

prec_hydrol_sn <- ggplot(presn, aes(x=hyear, y=csum_mean)) + 
  geom_hline(yintercept = meandf) + 
  geom_hline(yintercept = meandf + 2*sddf, color ='blue', linetype = 'dashed') +
  geom_hline(yintercept = meandf - 2*sddf, color ='red', linetype = 'dashed') +
  geom_hline(yintercept = meandf + 1*sddf, color ='blue', linetype = 'dotted') +
  geom_hline(yintercept = meandf  - 1*sddf, color ='red', linetype = 'dotted') +
  geom_errorbar(aes(ymin = csum_mean - csum_se, ymax= csum_mean + csum_se), width=.1, colour='gray') +
  geom_point(size=2) + theme_bw() +
  scale_x_continuous(breaks=seq(1950,2020, by=5)) +
  scale_y_continuous(breaks=seq(0,1500, by=250)) +
  geom_text_repel(
    data = subset(presn, csum_mean < (meandf - 1*sddf)),
    aes(label = hyear)) +
  theme(panel.grid.minor = element_blank()) +
  ylab('Cumulative Precipitation (hydrological year)') + xlab('year')

prec_hydrol_sn + annotation_custom(ggplotGrob(cp), xmin = 1990, xmax = 2020, ymin = 1050)
```

@@
